---
title: "Green Inlet Monitoring Verification"
author: "Monica Gucciardi"
date: "2025-07-22"
output: html_document
---

```{r setup, include=FALSE}
#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)
library(knitr)

#Database Stuff
library(pool)
library(RPostgres)
library(pwdgsi)

#Other stuff
library(digest)
options(stringsAsFactors=FALSE)

marsDBCon <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "mars_prod",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)},
  error = function(e){e})
```


## Introduction
This is a reimplementation of the green inlet monitoring data caclulation project, originally by Brian Cruice, in service of his and Johanna Batterton's investigation into hydraulic performance of Philadelphia's green inlets. This analysis will recalculate and replot the analyses performed for their original presentation on this issue at VUSP 2024. The analysis will make use of all updated data collected since that time - the VUSP analysis limited itself to data collected before 2023.

```{r Pulling site metrics and assembling calculation ranges, echo = FALSE}
wells <- dbGetQuery(marsDBCon, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id 
                    where o.ow_suffix like 'GI%'
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')")

wells <- filter(wells, ow_uid != 1077) #179-5-1 GI2 was not monitored

#Pulling system characteristics for calculations
snaps <- marsFetchSMPSnapshot(marsDBCon, wells$smp_id, wells$ow_suffix, "today")

#Pulling sumps directly to verify
sumpquery <- paste0("select o.ow_uid, o.smp_id, o.ow_suffix, l.sumpdepth_choice, v.sumpdepth_ft from fieldwork.tbl_ow o 
left join fieldwork.viw_ow_sumpdepth v on o.ow_uid = v.ow_uid
left join fieldwork.tbl_sumpdepth_lookup l on l.sumpdepth_lookup_uid = v.sumpdepth_lookup_uid
where o.ow_uid in (", paste(wells$ow_uid, collapse = ", "), ')')

sumps <- dbGetQuery(marsDBCon, sumpquery)

#Overflow calculations in green inlets require the cap-to-hook and hook-to-sensor measurements
#The value we want is called deployment_depth_ft in this view - the sum of the CTH and HTS measurements
cthquery <- paste0("select ow_uid, well_depth_ft, start_dtime, end_dtime, deployment_depth_ft
                   from fieldwork.viw_ow_plus_measurements where ow_uid in (", paste(wells$ow_uid, collapse = ", "), ')')
#Don't need to select by start and end time - we have only one measurement per well in this case.
cth <- dbGetQuery(marsDBCon, cthquery)

#Sensor monitoring range
boundaryquery <- paste0("select ow_uid, min(dtime) as mintime, max(dtime) as maxtime from data.tbl_ow_leveldata_raw
              where ow_uid in (", paste(wells$ow_uid, collapse = ", "), ')
              group by ow_uid')
boundaries <- dbGetQuery(marsDBCon, boundaryquery)


#Unified metrics table for GI-type well calculations
calctable <- left_join(wells, cth, by = "ow_uid") %>%
  select(-start_dtime, -end_dtime) %>%
  left_join(boundaries, by = "ow_uid")
```

## Green Inlet Overtopping

Green inlet overtopping is measured relative to the deployment depth of the sensor. The deployment depth is the sum of the measurement between the inlet grate and the sensor's hook (cap-to-hook) and the measurement between the sensor's hook and the sensor's aperture (hook-to-sensor). This value is stored in `fieldwork.viw_ow_plus_measurements` and is listed here.

`r kable(calctable)`

```{r pressure, echo=FALSE}
otmetrics <- data.frame(NULL)
for(i in 1:nrow(calctable)){
#for(i in 1){
 sitelevel <- dbGetQuery(marsDBCon, paste0("select * from data.tbl_ow_leveldata_raw where 
                          ow_uid = ",  calctable$ow_uid[i], 
                                            "and dtime >= '", calctable$mintime[i], "'",
                                            #"and dtime <= '", min(ymd("2023-01-01", tz = "America/New_York"), calctable$maxtime[i]), "'"))
                                            "and dtime <= '", calctable$maxtime[i], "'"))
  
 siteevents <- dbGetQuery(marsDBCon, paste0("select * from data.tbl_radar_event where
                                             radar_uid = ", calctable$radar_uid[i])) %>%
    filter(eventdatastart >= calctable$mintime[i],
           #eventdataend <= min(ymd("2023-01-01", tz = "America/New_York"), calctable$maxtime[i]))
           eventdataend <= calctable$maxtime[i])
  
  for(j in 1:nrow(siteevents)){
    eventdata <- filter(sitelevel, dtime >= siteevents$eventdatastart[j], dtime <= siteevents$eventdataend[j])
    eventmetric <- data.frame(ow_uid = calctable$ow_uid[i], 
                              radar_event_uid = siteevents$radar_event_uid[j], 
                              eventdatastart = siteevents$eventdatastart[j], 
                              eventdataend = siteevents$eventdataend[j],
                              overtop = marsOvertoppingCheck_bool(eventdata$level_ft, calctable$deployment_depth_ft[i]))
    otmetrics <- rbind(otmetrics, eventmetric)
  }
}

otmetrics %>% filter(overtop == "TRUE" | overtop == "FALSE") %>%
  group_by(ow_uid) %>%
  summarize(events = n(),
            overtopping = sum(as.logical(overtop)),
            overtopping_percent = sum(as.logical(overtop))/n() * 100) %>% left_join(calctable) %>% 
  select(smp_id, ow_suffix, events, overtopping, overtopping_percent) %>%
  kable

```

