---
title: "Green Inlet Monitoring Verification"
author: "Monica Gucciardi"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)
library(knitr)

#Database Stuff
library(pool)
library(RPostgres)
library(pwdgsi)

#Other stuff
library(digest)
library(openxlsx)
library(wesanderson)

options(stringsAsFactors=FALSE)

marsDBCon <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "mars_prod",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)},
  error = function(e){e})

# Brian's Season Function
season_fx <- function(date_time){
  x <- date_time
  x_day <- x %>% day()
  x_mon <- x %>% month()
  
  #spring, summer, fall, winter
  x <- ifelse(x_mon == 4 | x_mon == 5 | (x_mon == 3 & x_day > 20) | (x_mon == 6 & x_day < 21),
              "Spring",
              
       ifelse((x_mon == 6 & x_day > 20) | x_mon == 7 | x_mon == 8 | (x_mon == 9 & x_day < 21),
              "Summer",
       
       ifelse((x_mon == 9 & x_day > 20) | x_mon == 10 | x_mon == 11 | (x_mon ==12 & x_day < 21),
              "Autumn",
              "Winter")))
  
  return(x)
  
}
```

```{r func}
overtopping_qmax_plot <- function(data, design_storm, system_chars, event_dates = NULL, event_descriptions = NULL){
  #Sbrowser()
  #clean dates for x-axis
  # date_formats <- c(guess_formats(data$eventdatastart, "mdy HMS"),
  #                   guess_formats(data$eventdatastart, "mdy"))
  # dates_x <- data$eventdatastart %>% lubridate::as_datetime(format = date_formats)
  # 
  # data$eventdatastart <- dates_x
  # event_dates <- event_dates %>% lubridate::mdy() %>% lubridate::as_datetime()
  min_date <- min(data$eventdatastart)
  max_date <- max(data$eventdatastart)
  
  data$overtop <- as.logical(data$overtop)
  
  event_dates <- event_dates %>% mdy %>% force_tz(tzone = "America/New_York")
  
  #Set overtop to sizes
  data$overtop_sz[data$overtop == FALSE] <- as.numeric(2)
  data$overtop_sz[data$overtop == TRUE] <- as.numeric(4)
  data$overtop_col[data$overtop == FALSE] <- wes_palettes$Royal1[1]
  data$overtop_col[data$overtop == TRUE] <- wes_palettes$Royal1[2]
  
  #subset of data exceeding design stor
  data_ovr_design <- data %>% dplyr::filter(eventdepth_in > design_storm)
  data <- data %>% mutate("ExceedDesignStorm" = ifelse(eventdepth_in > design_storm,"True",NA))
  
  
  # qmax value
  qmax <- system_chars$`Max.Flow.w/.Perforations.(CFS)` %>% as.numeric() %>% round(2)
  
  # y-max value
  ymax_obs <- max(c(data$qpeak,qmax), na.rm = TRUE)*1.1 # buffer for higher qpeak values
  
  plot_x <- ggplot(data,
                   aes(x = eventdatastart,
                       y = qpeak)) +
    geom_point(aes(color = overtop,
                   size = overtop)) + 
    
    scale_color_manual(values = c(wes_palettes$Royal1[2], wes_palettes$Royal1[1])) +
    scale_size_manual(values = c(as.numeric(4), as.numeric(2)))
    
    
    if(length(event_dates) > 0 & length(event_descriptions) > 0){
      for(i in 1:length(event_dates)){
        plot_x <- plot_x + geom_vline(xintercept = event_dates[i], color = wes_palettes$Royal1[4], linewidth = 1.1, linetype = "dashed") +
          geom_text(label = event_descriptions[i], angle = 90,
                    y = 2.7, color = "black", size = 12 / .pt, hjust = "left",
                    x = as.numeric(event_dates[i] + days(14)))
      }
      
    }
    
  plot_x <- plot_x +  geom_hline(yintercept = qmax, color = wes_palettes$Royal1[4], size = 1.5) +
                      scale_y_continuous(limits = c(0,ymax_obs), minor_breaks =seq(0,max(3,ymax_obs),0.2)) +
                      scale_x_datetime(date_minor_breaks = "2 months") +
                      ylab("Event Qpeak (cfs)") + xlab("Event Date/Time") +
                      geom_text(label = paste0("System Distribution Pipe Qmax: ",qmax," cfs"),
                                y = (qmax*1.05), color = "black", size = 12 / .pt, hjust = "left",
                                x = data$eventdatastart[round(0.05*length(data$eventdatastart))]) +
                      ggtitle(paste0("Event Peak Flow Rate and Overtopping vs Time for ",data$smp_id[1])) +
                      
                      #add design storm values
                      geom_point(aes(x = eventdatastart,
                                     y = qpeak, size = factor(overtop),  color = factor(overtop), shape = factor(ExceedDesignStorm))) +
                      scale_shape_manual(name = paste0("Exceeds Design Storm Depth: ",round(design_storm,2)," in"), values = c(2), labels = c("True"), na.translate = FALSE) +
                      scale_color_manual(name = "Overtopping", values = wes_palettes$Royal1, labels = c("False","True"), guide = guide_legend(reverse = TRUE)) +
                      scale_size_manual(name = "Overtopping", values = c(2,4), labels = c("False","True"), guide = guide_legend(reverse = TRUE)) +
                      #from pwdgsi plotsS
                      ggplot2::theme(
                        #text = element_text(size = rel(2)), #size previously set to 16
                        axis.title.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
                        axis.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of x axis text #size previously set to 14
                        axis.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of y axis text
                        panel.background =  ggplot2::element_rect(fill = wes_palettes$Royal1[3], colour = NA), # set white background
                        panel.border =      ggplot2::element_rect(fill = NA, colour="black"), # set black border
                        panel.grid.major =  ggplot2::element_line(colour = "grey70", linewidth = 0.5), # set major grid lines
                        panel.grid.minor =  ggplot2::element_line(colour = "grey90", linewidth = 0.5), # set minor grid lines
                        legend.position = "bottom", #format legend (to be compiled with rainfall plot in grid.arrange())
                        legend.text = ggplot2::element_text(size = ggplot2::rel(.9)))
  
  
  return(plot_x)
  
}

pipejet_overtop_plot <- function(data, design_storm){
  
  #clean dates for x-axis
  data <- data %>% dplyr::filter(!is.na(last_jet))
  
  # data$last_jet <- data$eventdatastart %>% lubridate::mdy_hm()
  # event_dates <- event_dates %>% lubridate::mdy() %>% lubridate::as_datetime()
  # min_date <- min(lubridate::date(data$last_jet))
  # max_date <- max(lubridate::date(data$last_jet))
  
  
  data$overtop <- as.logical(data$overtop)
  
  #Set overtop to sizes
  data$overtop_sz[data$overtop == FALSE] <- as.numeric(2)
  data$overtop_sz[data$overtop == TRUE] <- as.numeric(4)
  data$overtop_col[data$overtop == FALSE] <- wes_palettes$Royal1[1]
  data$overtop_col[data$overtop == TRUE] <- wes_palettes$Royal1[2]
  
  #subset of data exceeding design stor
  data_ovr_design <- data %>% dplyr::filter(eventdepth_in > design_storm)
  data <- data %>% mutate("ExceedDesignStorm" = ifelse(eventdepth_in > design_storm,"True",NA))
  # y-max value
  ymax_obs <- max(data$eventpeakintensity_inhr, na.rm = TRUE)
  
  
  plot_x <- ggplot(data,
                   aes(x = last_jet,
                       y = eventpeakintensity_inhr)) +
    geom_point(aes(color = factor(overtop),
                   size = factor(overtop))) +
    geom_hline(yintercept = 2.5, color = wes_palettes$Royal1[4], linewidth = 1.5) +
    scale_y_continuous(limits = c(0,max(3.6,ymax_obs)), minor_breaks =seq(0,max(3,ymax_obs),0.2)) +
    ylab("Event Peak Intensity (in/hr)") + xlab("Days Since Last Pipe Jetting") +
    geom_text(label = "Philadelphia 1-year, 15-minute Peak Intensity: 2.5 in/hr",
              y = 2.6, color = "black", size = 12 / .pt, hjust = "left",
              # x = data$last_jet[round(0.05*length(data$last_jet))]) +
              x = max(data$last_jet)*0.05) +
    ggtitle(paste0("Event Peak Intensity and Overtopping vs Days Since Pipe Jetting for ",data$smp_id[1])) +
    
    #add design storm values
    geom_point(aes(x = last_jet,
                   y = eventpeakintensity_inhr, size = factor(overtop),  color = factor(overtop), shape = factor(ExceedDesignStorm))) +
    scale_shape_manual(name = paste0("Exceeds Design Storm Depth: ",round(design_storm,2)," in"), values = c(2), labels = c("True"), na.translate = FALSE) +
    scale_color_manual(name = "Overtopping", values = wes_palettes$Royal1, labels = c("False","True"), guide = guide_legend(reverse = TRUE)) +
    scale_size_manual(name = "Overtopping", values = c(2,4), labels = c("False","True"), guide = guide_legend(reverse = TRUE)) +
    #from pwdgsi plots
    ggplot2::theme(
      #text = element_text(size = rel(2)), #size previously set to 16
      axis.title.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
      axis.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of x axis text #size previously set to 14
      axis.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of y axis text
      panel.background =  ggplot2::element_rect(fill = wes_palettes$Royal1[3], colour = NA), # set white background
      panel.border =      ggplot2::element_rect(fill = NA, colour="black"), # set black border
      panel.grid.major =  ggplot2::element_line(colour = "grey70", linewidth = 0.5), # set major grid lines
      panel.grid.minor =  ggplot2::element_line(colour = "grey90", linewidth = 0.5), # set minor grid lines
      legend.position = "bottom", #format legend (to be compiled with rainfall plot in grid.arrange())
      legend.text = ggplot2::element_text(size = ggplot2::rel(.9)))
  

  
  return(plot_x)
  
}

```

## Introduction
This is a reimplementation of the green inlet monitoring data caclulation project, originally by Brian Cruice, in service of his and Johanna Batterton's investigation into hydraulic performance of Philadelphia's green inlets. This analysis will recalculate and replot the analyses performed for their original presentation on this issue at VUSP 2024. The analysis will make use of all updated data collected since that time - the VUSP analysis limited itself to data collected before 2023.

```{r Pulling Green Inlet site metrics and assembling calculation ranges, echo = FALSE}
inlets <- dbGetQuery(marsDBCon, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id 
                    where o.ow_suffix like 'GI%'
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')")

inlets <- filter(inlets, ow_uid != 1077) #179-5-1 GI2 was not monitored

#Overflow calculations in green inlets require the cap-to-hook and hook-to-sensor measurements
#The value we want is called deployment_depth_ft in this view - the sum of the CTH and HTS measurements
cthquery <- paste0("select ow_uid, well_depth_ft, start_dtime, end_dtime, deployment_depth_ft
                   from fieldwork.viw_ow_plus_measurements where ow_uid in (", paste(inlets$ow_uid, collapse = ", "), ')')
#Don't need to select by start and end time - we have only one measurement per well in this case.
#If we ever do get multiple deployment depth values per well here, we will need to be responsive to that
#Be careful!
cth <- dbGetQuery(marsDBCon, cthquery)

#Sensor monitoring range
boundaryquery <- paste0("select ow_uid, min(dtime) as mintime, max(dtime) as maxtime from data.tbl_ow_leveldata_raw
              where ow_uid in (", paste(inlets$ow_uid, collapse = ", "), ')
              group by ow_uid')
boundaries <- dbGetQuery(marsDBCon, boundaryquery)


#Unified metrics table for GI-type well calculations
calctable <- left_join(inlets, cth, by = "ow_uid") %>%
  select(-start_dtime, -end_dtime) %>%
  left_join(boundaries, by = "ow_uid")

#Date Overrides
#System 1-1 short circuiting observed on 11/13/2020, so cut data off here
calctable$maxtime[calctable$smp_id == '1-1-1'] <- ymd_hms('2020-11-13 00:00:00', tz = "America/New_York")

#System 439-1-1 short circuiting observed on 2022-01-14, so cut data off here
calctable$maxtime[calctable$smp_id == '439-1-1'] <- ymd_hms('2022-01-14 00:00:00', tz = "America/New_York")


#System 179-5 had its distribution pipe capped for a period of two months
exclusions <- calctable %>%
  select(ow_uid, smp_id, ow_suffix, mintime, maxtime) %>%
  mutate(mintime = NA_Date_,
         maxtime = NA_Date_)

exclusions$mintime[exclusions$smp_id == '179-5-1'] <- ymd_hms('2021-11-08 00:00:00',  tz = "America/New_York")
exclusions$maxtime[exclusions$smp_id == '179-5-1'] <- ymd_hms('2021-12-30 00:00:00',  tz = "America/New_York")

```

```{r Pulling Corresponding OW metrics and ranges, echo = FALSE}
wells <- dbGetQuery(marsDBCon, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id 
                    where o.ow_suffix = 'OW1'
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')")

#Pulling sumps directly
sumpquery <- paste0("select o.ow_uid, o.smp_id, o.ow_suffix, l.sumpdepth_choice, v.sumpdepth_ft from fieldwork.tbl_ow o 
left join fieldwork.viw_ow_sumpdepth v on o.ow_uid = v.ow_uid
left join fieldwork.tbl_sumpdepth_lookup l on l.sumpdepth_lookup_uid = v.sumpdepth_lookup_uid
where o.ow_uid in (", paste(wells$ow_uid, collapse = ", "), ')')

sumps <- dbGetQuery(marsDBCon, sumpquery) %>% distinct

#Pull the deployment depths (cap to hook and hook to sensor) to assist with head differential calculations
well_cthquery <- paste0("select ow_uid, well_depth_ft, start_dtime, end_dtime, deployment_depth_ft
                   from fieldwork.viw_ow_plus_measurements where ow_uid in (", paste(wells$ow_uid, collapse = ", "), ')')
well_cth <- dbGetQuery(marsDBCon, well_cthquery)

#There are multiple measurements at some wells, with date ranges for when they are active. 
#We will need to be careful when we perform the head differential calculations.
#Be careful!

#NA end dates mean the measurement is still valid
#Be careful!
well_cth$end_dtime[is.na(well_cth$end_dtime)] <- lubridate::now(tz = "America/New_York")

#Assemble the corresponding metrics table for calculations
wellboundaries <- select(calctable, smp_id, mintime, maxtime)
welltable <- left_join(wells, wellboundaries, by = "smp_id") %>%
  left_join(sumps, by = c("ow_uid", "smp_id", "ow_suffix"))

```

```{r Read manually-collected metadata for inlet types end elevations}

#Asbuilt elevations
#These are necessary to measure head-differential calculations
asbuilt_file <- "//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/relative_elevations.xlsx"
asbuilt_elev <- openxlsx::read.xlsx(xlsxFile = asbuilt_file, sheet = "elev") %>%
  select(ow_uid, as_built_elev)

#Inlet metadata
inlet_type <- openxlsx::read.xlsx(xlsxFile = "//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/Assets.xlsx",
                                  sheet = "Inlet Depths")

#System characteristics
sys_char <- openxlsx::read.xlsx(xlsxFile = "//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/SystemCharacteristics.xlsx",
                            sheet = "Characteristics")

#Inlet traps
trap_status <- inlet_type %>% dplyr::select(ow_uid, Trap, drainage_area_sf)

#Design storm sizes
stormsizemanaged <- select(sys_char, smp_id, stormsizemanaged_in = `Storm.Size.Managed.(in)`)


```

## Green Inlet Overtopping

Green inlet overtopping is measured relative to the deployment depth of the sensor. The deployment depth is the sum of the measurement between the inlet grate and the sensor's hook (cap-to-hook) and the measurement between the sensor's hook and the sensor's aperture (hook-to-sensor). This value is stored in `fieldwork.viw_ow_plus_measurements` and is listed here.

`r kable(calctable)`

```{r Green Inlet Overtopping, echo=FALSE, include = FALSE}
otmetrics <- data.frame(NULL)
for(i in 1:nrow(calctable)){
#for(i in 1){

 #Pull the Green Inlet data for the site
 sitelevel <- dbGetQuery(marsDBCon, paste0("select * from data.tbl_ow_leveldata_raw where 
                          ow_uid = ",  calctable$ow_uid[i], 
                                            "and dtime >= '", calctable$mintime[i], "'",
                                            "and dtime <= '", calctable$maxtime[i], "'"))

 #Pull the rain events for the site
 siteevents <- dbGetQuery(marsDBCon, paste0("select * from data.tbl_radar_event where
                                             radar_uid = ", calctable$radar_uid[i])) %>%
    filter(eventdatastart >= calctable$mintime[i],
           eventdataend <= calctable$maxtime[i])
 
 #Does this GI have an exclusion date range?
 excludeflag <- !is.na(exclusions$mintime[exclusions$ow_uid == calctable$ow_uid[i]])
 if(excludeflag == TRUE){
   exclude_min <- exclusions$mintime[exclusions$ow_uid == calctable$ow_uid[i]]
   exclude_max <- exclusions$maxtime[exclusions$ow_uid == calctable$ow_uid[i]]
   
   sitelevel <- filter(sitelevel, dtime < exclude_min | dtime > exclude_max)
   siteevents <- filter(siteevents, eventdatastart < exclude_min | eventdatastart > exclude_max)
 }
  
  for(j in 1:nrow(siteevents)){
    eventdata <- filter(sitelevel, dtime >= siteevents$eventdatastart[j], dtime <= siteevents$eventdataend[j])
    
    #If there was no data collected for this event, skip it
    if(nrow(eventdata) == 0){
      next
    }
    
    eventmetric <- data.frame(ow_uid = calctable$ow_uid[i], 
                              radar_event_uid = siteevents$radar_event_uid[j], 
                              eventdatastart = siteevents$eventdatastart[j], 
                              eventdataend = siteevents$eventdataend[j],
                              maxlevel_ft = max(eventdata$level_ft), #Store this for the head differential calculations later
                              maxlevel_dtime = eventdata$dtime[eventdata$level_ft == max(eventdata$level_ft)], #Ditto
                              overtop = marsOvertoppingCheck_bool(eventdata$level_ft, calctable$deployment_depth_ft[i]))
    otmetrics <- rbind(otmetrics, eventmetric)
    
  }
}

otsummary <- otmetrics %>%
  group_by(ow_uid) %>%
  summarize(events = n(),
            overtopping = sum(as.logical(overtop)),
            overtopping_pct = sum(as.logical(overtop))/n() * 100) %>% left_join(calctable, by = "ow_uid") %>% 
  select(smp_id, ow_suffix, events, overtopping, overtopping_pct)

```

`r kable(otsummary)`


```{r Head differential calculations, echo = FALSE, include = FALSE}
#Find the corresponding level in the OW when the GI was at its peak
hdraw <- data.frame(NULL)

for(i in 1:nrow(welltable)){
  well_smp <- welltable$smp_id[i]
  well_uid <- welltable$ow_uid[i]
  
  inlet_uid <- filter(calctable, smp_id == well_smp) %>% pull(ow_uid)
  inlet_smp <- filter(calctable, ow_uid == inlet_uid) %>% pull(smp_id) #just to verify
  
  #Pull the OW data for the site
  welllevel <- dbGetQuery(marsDBCon, paste0("select * from data.tbl_ow_leveldata_raw where 
                          ow_uid = ",  well_uid, 
                                            "and dtime >= '", welltable$mintime[i], "'",
                                            "and dtime <= '", welltable$maxtime[i], "'"))
  
  siteevents <- filter(otmetrics, ow_uid == inlet_uid) %>%
    mutate(welllevel_ft = NA, 
           welldtime = as.POSIXct(NA, tz = "America/New_York"), #Ask me how I know this needs an explicit time zone ( TT_TT)
           difftime = NA,
           well_uid = well_uid)
    

  for(j in 1:nrow(siteevents)){
    eventlevel <- filter(welllevel, between(dtime, siteevents$eventdatastart[j], siteevents$eventdataend[j]))
    
    if(nrow(eventlevel) == 0){
      print(paste(well_smp, "OW1 has no data for the period when", inlet_smp, "GI1 has data. That range is",
                  siteevents$eventdatastart[j], "to", siteevents$eventdataend[j]))
      next
    }
    
    #The inlet and OW might have different sample periods, so time at which the inlet peaks might not be in eventlevel$dtime
    #So we instead find the closest time by taking the difference between eventlevel$dtime and siteevents$maxlevel_dtime
    diffs <- abs(eventlevel$dtime - siteevents$maxlevel_dtime[j])
    well_maxindex <- which.min(diffs)
    
    siteevents$welldtime[j] <- eventlevel$dtime[well_maxindex]
    siteevents$welllevel_ft[j] <- eventlevel$level_ft[well_maxindex]
    siteevents$difftime[j] <- diffs[well_maxindex]

  }
  
  hdraw <- rbind(hdraw, siteevents)
}

#Compute head differentials in accordance with the method on page 12 of this document
# "\\pwdoows\oows\Watershed Sciences\GSI Monitoring\03 Reports and Presentations\02 Conferences\2024\Villanova Symposium 2024\Presentations\Batterton\Batterton_VUSP Symposium 2024.pdf"

hd_elevs <- hdraw %>% 
  #Attach the as-built elevations to the event records
  left_join(asbuilt_elev, by = "ow_uid") %>% #ow_uid is the inlet UID
  mutate(inlet_elev_ft = as_built_elev) %>%
  select(-as_built_elev) %>%
  left_join(asbuilt_elev, by = c("well_uid" = "ow_uid")) %>%
  mutate(well_elev_ft = as_built_elev) %>%
  select(-as_built_elev)

#Attach the deployment depths to the event records
#For inlets, this is easy, since we only have one per ow_uid
hd_elevs <- select(calctable, ow_uid, smp_id, inlet_deploy_ft = deployment_depth_ft) %>%
  right_join(hd_elevs)

#For wells, this will require iteration to be responsive to the validity date range.
#Be careful!
#If we ever got multiple well measurements at a green inlet, we would need to do this there, too
hd_elevs$well_deploy_ft <- NA_real_
for(i in 1:nrow(well_cth)){
  #Criteria range is complicated so let's compute them outside of the assignment statement
  event_at_correct_well <- hd_elevs$well_uid == well_cth$ow_uid[i]
  event_within_deployment_range <- between(hd_elevs$eventdatastart, well_cth$start_dtime[i], well_cth$end_dtime[i])
  
  #both vectors must be true to assign the deployment depth
  hd_elevs$well_deploy_ft[event_at_correct_well & event_within_deployment_range] <- well_cth$deployment_depth_ft[i]
}

headdiffs <- hd_elevs %>%
         #headdiff_ft: Head differential at peak inlet water level
  mutate(headdiff_ft = (inlet_elev_ft - inlet_deploy_ft + maxlevel_ft) - (well_elev_ft - well_deploy_ft + welllevel_ft)) %>%
  group_by(ow_uid) %>%
  summarize(#maxdiff_ft: Theoretical maximum head differential - if inlet was full and well was empty
         maxdiff_ft = max(headdiff_ft, na.rm = TRUE)) %>%
  right_join(hd_elevs) %>%
        #normaldiff: Percent of the maximum differential reached at that event (unitless, between 0 and 1)
  mutate(headdiff_ft = (inlet_elev_ft - inlet_deploy_ft + maxlevel_ft) - (well_elev_ft - well_deploy_ft + welllevel_ft)) %>%
  mutate(normaldiff = headdiff_ft/maxdiff_ft) %>%
  select(ow_uid, well_uid, smp_id, radar_event_uid, eventdatastart, eventdataend, overtop, headdiff_ft, maxdiff_ft, normaldiff)

```

```{r Plots!, echo = FALSE, include = FALSE}
#Several plots require rain event metadata that we have discarded by now
rain_event_metadata <- dbGetQuery(marsDBCon, "select radar_uid, radar_event_uid, eventdatastart, eventdataend, eventpeakintensity_inhr, eventdepth_in, eventavgintensity_inhr from data.tbl_radar_event") %>%
  filter(eventdatastart >= min(calctable$mintime), 
         eventdataend <= max(calctable$maxtime),
         radar_uid %in% calctable$radar_uid) %>%
  select(-eventdatastart, -eventdataend)

#Attach event metadata
headdiffs_plot <- left_join(headdiffs, rain_event_metadata, by = "radar_event_uid") %>%
  mutate(season = season_fx(eventdatastart)) %>% #And seasons
  left_join(trap_status) %>% #and inlet trap metadata
  left_join(stormsizemanaged)

#For now, since we don't have updated work orders for pipe jetting, we will filter our events to those same ones from Villanova's date range

headdiffs_villanova <- filter(headdiffs_plot, eventdatastart <= ymd('2023-01-01', tz = "America/New_York")) %>%
  filter(eventdepth_in <= stormsizemanaged_in)

villanova_table <- headdiffs_villanova %>%
  group_by(ow_uid) %>%
  summarize(events = n(),
            meandepth_in = mean(eventdepth_in),
            overtopping = sum(as.logical(overtop)),
            overtopping_pct = sum(as.logical(overtop))/n()) %>% left_join(calctable, by = "ow_uid") %>% 
  select(smp_id, meandepth_in, events, overtopping, overtopping_pct)

full_table <- headdiffs_plot %>%
  group_by(ow_uid) %>%
  summarize(events = n(),
            meandepth_in = mean(eventdepth_in),
            overtopping = sum(as.logical(overtop)),
            overtopping_pct = sum(as.logical(overtop))/n()) %>% left_join(calctable, by = "ow_uid") %>% 
  select(smp_id, meandepth_in, events, overtopping, overtopping_pct)


#Pipe jetting dates
graph_dates <- read_csv("//pwdoows/oows/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/graph_dates.csv")


for(i in 1:nrow(calctable)){
  sitedata <- filter(headdiffs_villanova, ow_uid == calctable$ow_uid[i])
  sys_id <- calctable$smp_id[i] %>% str_replace("(\\d+-\\d+)-\\d+", "\\1")
  
  site_dates <- filter(graph_dates, system_id == sys_id, graph == TRUE) %>%
    filter(!is.na(date_complete)) %>%
    select(system_id, date_complete, graph_text) %>%
    filter(graph_text == "Pipe Jetting")
  
  if(sys_id == "1-1"){
    site_dates <- filter(site_dates, date_complete != "3/11/2019")
  }
  
  design_storm <- dbGetQuery(marsDBCon,
                           paste0("SELECT sys_creditedstormsizemanaged_in FROM external.tbl_systembdv
                                  WHERE system_id = '",sys_id,"'")) %>% pull
  
  plotdata <- sitedata %>% dplyr::filter(eventdepth_in <= design_storm)
  
  loc_sys_char <- sys_char %>% dplyr::filter(smp_id == calctable$smp_id[i])
  
  # calculate qpeak; rational method using peak intensity as i. Q= CiA. Use full system drainage area for distr. pipe
  plotdata$qpeak <- plotdata$eventpeakintensity_inhr*0.95*loc_sys_char$`System.Drainage.Area.(SF)` * (1/12) * (1/3600) # last terms to cfs

  qpeak_plot <- overtopping_qmax_plot(data =plotdata, 
                                      design_storm = design_storm,
                                      system_chars = loc_sys_char,
                                      event_dates = site_dates$date_complete,
                                      event_descriptions = site_dates$graph_text)
  
  ggsave(plot = qpeak_plot,
         filename = paste0("plots/",calctable$smp_id[i],"_qpeak.png"),
         width = 2100, height = 1620, units = "px")
  
  
  #Pipe jetting
  for(j in 1:nrow(plotdata)){
    
    #get the current date in question
    date_x <- plotdata$eventdatastart[j] %>% ymd_hms()
    
    # list of dates where pipe jetting occurred, coerced into datetime format
    jet_days <- site_dates$date_complete %>% mdy() %>% as_datetime()
    
    # Find the number of days between the current date and each pipe jetting event
    time_difs <- difftime(date_x, jet_days, units = "days")
    
    # Remove pipe jetting events happening in the future; limit it to a list of past pipe jetting events
    time_difs <- time_difs[time_difs > 0]
    
    # Find the shortest distance in days since a pipe jetting event. Set to NA if none are found.
    plotdata$last_jet[j] <- ifelse(length(time_difs) > 0,
                                    min(time_difs),
                                    NA)
    
  }
  
  plot_zds <- pipejet_overtop_plot(data = plotdata, 
                                   design_storm = design_storm)
  
  ggsave(plot = plot_zds,
         filename = paste0("plots/",calctable$smp_id[i],"_days_since_jetting.png"),
         width = 2100, height = 1620, units = "px")
}


```


```{r More Plots!, echo = FALSE, include = FALSE}
headdiffs_plot <- filter(headdiffs_villanova, normaldiff > 0)

headdiffs_plot$inlet_style[headdiffs_plot$Trap == FALSE] <- "New (Without Trap)"
headdiffs_plot$inlet_style[headdiffs_plot$Trap == TRUE] <- "Old (with Trap)"


label_text <- headdiffs_plot %>%
              dplyr::group_by(inlet_style) %>%
              summarize(style_count = n()) %>%
              ungroup() %>%
              right_join(headdiffs_plot, by = "inlet_style") %>%
              dplyr::group_by(inlet_style, overtop) %>%
              summarize(label = paste0(round(100*n()/style_count,0),"%"),
                        normaldiff = max(normaldiff)) %>%
              dplyr::select(inlet_style,overtop,label, normaldiff) %>%
              dplyr::distinct()

hdif_inlet_ot_bplot <- ggplot(data = headdiffs_plot, aes(y = normaldiff, x = inlet_style, fill = overtop)) +
                        geom_boxplot(size = 1.1, outlier.shape = NA) +
                        geom_point(position=position_jitterdodge(jitter.width = 0.1), shape = 21, alpha = 0.7, size = 1.5) +
                        xlab("Inlet Type") + ylab("Head Differential at Peak Water Level in Green Inlet (ft)") +
                        ggtitle("Head Differential by Inlet Type") +
                        scale_color_manual(values = c("darkgray","black")) + 
                        scale_fill_manual(values = wes_palettes$Moonrise2) + 
                        
                        geom_label(data = label_text, label = label_text$label, position = position_dodge(width = .8),
                                   hjust = "center", color = "white", fontface = "bold", show.legend = FALSE, label.size = 1.2) +
                        
                        
                        #from pwdgsi plots; house style
                        ggplot2::theme(
                          #text = element_text(size = rel(2)), #size previously set to 16
                          axis.title.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
                          axis.title.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
                          title = ggplot2::element_text(size = ggplot2::rel(1.4), color = "black"),
                          axis.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of x axis text #size previously set to 14
                          axis.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of y axis text
                          panel.background =  ggplot2::element_rect(fill = "white", colour = NA), # set white background
                          panel.border =      ggplot2::element_rect(fill = NA, colour="black"), # set black border
                          panel.grid.major =  ggplot2::element_line(colour = "grey70", size = 0.5), # set major grid lines
                          panel.grid.minor =  ggplot2::element_line(colour = "grey90", size = 0.5), # set minor grid lines
                          legend.position = "bottom", #format legend (to be compiled with rainfall plot in grid.arrange())
                          legend.text = ggplot2::element_text(size = ggplot2::rel(.9)))

hdif_inlet_ot_bplot

#Pipe slope

headdiffs_design <- left_join(headdiffs_plot, sys_char, by = "smp_id")

# By pipe slope
slope_x <- headdiffs_design$`Distrib..Slope.(%)` == 0.5
slope_x <- factor(slope_x, ordered = TRUE, levels = c(TRUE, FALSE))
headdiffs_design$Distribution_slope <- slope_x


# by pipe slope labels
label_text <- headdiffs_design %>%
  dplyr::group_by(Distribution_slope) %>%
  summarize(slope_count = n()) %>%
  ungroup() %>%
  right_join(headdiffs_design, by = c("Distribution_slope")) %>%
  dplyr::group_by(overtop, Distribution_slope) %>%
  summarize(label = paste0(round(100*n()/slope_count,0),"%"),
            normaldiff = max(normaldiff)) %>%
  dplyr::select(overtop,Distribution_slope,label, normaldiff) %>%
  dplyr::distinct()

label_text$normaldiff <- max(label_text$normaldiff, na.rm = TRUE)


ot_hdif_norm_slope_bplot_des <- ggplot(data = headdiffs_design, aes(y = normaldiff, x = Distribution_slope, fill = overtop)) +
  geom_boxplot(size = 1.1, outlier.shape = NA) +
  geom_point(position=position_jitterdodge(jitter.width = 0.1), shape = 21, alpha = 0.7, size = 1.5) +
  xlab("Sloped Distribution Pipe") + ylab("Normalized Head Dif. at Peak Water Level in Green Inlet") +
  ggtitle("Overtopping by Head Differential and Distribution Pipe Slope") +
  scale_fill_manual(values = c("grey41","grey82")) + 
  scale_fill_manual(values = wes_palettes$Moonrise2) + 
  
  geom_label(data = label_text, label = label_text$label, position = position_dodge(width = .8),
             hjust = "center", color = "white", fontface = "bold", show.legend = FALSE, label.size = 1.2) +
  
  #from pwdgsi plots; house style
  ggplot2::theme(
    #text = element_text(size = rel(2)), #size previously set to 16
    axis.title.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
    axis.title.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
    title = ggplot2::element_text(size = ggplot2::rel(1.4), color = "black"),
    axis.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of x axis text #size previously set to 14
    axis.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of y axis text
    panel.background =  ggplot2::element_rect(fill = "white", colour = NA), # set white background
    panel.border =      ggplot2::element_rect(fill = NA, colour="black"), # set black border
    panel.grid.major =  ggplot2::element_line(colour = "grey70", size = 0.5), # set major grid lines
    panel.grid.minor =  ggplot2::element_line(colour = "grey90", size = 0.5), # set minor grid lines
    legend.position = "bottom", #format legend (to be compiled with rainfall plot in grid.arrange())
    legend.text = ggplot2::element_text(size = ggplot2::rel(.9)))

ot_hdif_norm_slope_bplot_des

## By system

#by system labels
label_text <- headdiffs_design %>%
  dplyr::group_by(system_id) %>%
  summarize(sys_count = n()) %>%
  ungroup() %>%
  right_join(headdiffs_design, by = c("system_id")) %>%
  dplyr::group_by(overtop, system_id) %>%
  summarize(label = paste0(round(100*n()/sys_count,0),"%"),
            normaldiff = max(normaldiff)) %>%
  dplyr::select(overtop,system_id,label, normaldiff) %>%
  dplyr::distinct()

label_text$normaldiff <- max(label_text$normaldiff, na.rm = TRUE)

ot_hdif_norm_system_bplot_des <- ggplot(data = headdiffs_design, aes(y = normaldiff, x = system_id, fill = overtop)) +
  geom_boxplot(size = 1.1, outlier.shape = NA) +
  geom_point(position=position_jitterdodge(jitter.width = 0.1), shape = 21, alpha = 0.7, size = 1.5) +
  xlab("System ID") + ylab("Normalized Head Dif. at Peak Water Level in Green Inlet") +
  ggtitle("Overtopping by Head Differential per System") +
  scale_color_manual(values = c("darkgray","black")) + 
  scale_fill_manual(values = wes_palettes$Moonrise2) + 
  
  geom_label(data = label_text, label = label_text$label, position = position_dodge(width = .8),
             hjust = "center", color = "white", fontface = "bold", show.legend = FALSE, label.size = 1.2) +
  
  #from pwdgsi plots; house style
  ggplot2::theme(
    #text = element_text(size = rel(2)), #size previously set to 16
    axis.title.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
    axis.title.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"),
    title = ggplot2::element_text(size = ggplot2::rel(1.4), color = "black"),
    axis.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of x axis text #size previously set to 14
    axis.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), color = "black"), # set font size and color of y axis text
    panel.background =  ggplot2::element_rect(fill = "white", colour = NA), # set white background
    panel.border =      ggplot2::element_rect(fill = NA, colour="black"), # set black border
    panel.grid.major =  ggplot2::element_line(colour = "grey70", size = 0.5), # set major grid lines
    panel.grid.minor =  ggplot2::element_line(colour = "grey90", size = 0.5), # set minor grid lines
    legend.position = "bottom", #format legend (to be compiled with rainfall plot in grid.arrange())
    legend.text = ggplot2::element_text(size = ggplot2::rel(.9)))

ot_hdif_norm_system_bplot_des

ggsave(filename = paste0("plots/Head_dif_vs_Inlet_type.png"), plot = hdif_inlet_ot_bplot, width = 10, height = 8)
ggsave(filename = paste0("plots/Head_dif_vs_slope_design_storms.png"), plot = ot_hdif_norm_slope_bplot_des, width = 10, height = 8)
ggsave(filename = paste0("plots/Head_dif_vs_system_design_storms.png"), plot = ot_hdif_norm_system_bplot_des, width = 10, height = 8)


```
