---
title: "Database Diffs"
output: html_document
date: "2025-09-22"
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)

#Database Stuff
library(pool)
library(openxlsx)
library(RPostgres)
library(pwdgsi)

#Brian's archival database
mars_archive <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "20240405T2000_mars_data",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = "EST")},
  error = function(e){e})

#Live database
mars_prod <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "mars_prod",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)},
  error = function(e){e})


#Calculation data ranges
  #Basic cutoff date
  start_date <- ymd("2019-01-01", tz = "America/New_York")
  cutoff_date <- ymd("2024-01-01", tz = "America/New_York") #Original analysis was 2019 through 2023
  
  #Site-specific cutoff dates
  cutoff_11 <- ymd("2020-11-13", tz = "America/New_York") #System 1-1 taken offline for short-circuiting
  cutoff_4391 <- ymd("2022-01-14", tz = "America/New_York") #System 439-1 taken offline for short-circuiting
  
  #Site-specific exclusion ranges
  capped_1795 <- ymd("2021-11-08", tz = "America/New_York") #System 179-5 was capped for 2 months
  uncapped_1795 <- ymd("2021-12-30", tz = "America/New_York")
  exclusion_1795 <- interval(start = capped_1795, end = uncapped_1795)

  #Cutoff Dates - Archive
  #Basic cutoff date
  start_date_archive <- ymd("2019-01-01", tz = "EST")
  cutoff_date_archive <- ymd("2024-01-01", tz = "EST") #Original analysis was 2019 through 2023
  
  #Site-specific cutoff dates
  cutoff_11_archive <- ymd("2020-11-13", tz = "EST") #System 1-1 taken offline for short-circuiting
  cutoff_4391_archive <- ymd("2022-01-14", tz = "EST") #System 439-1 taken offline for short-circuiting
  
  #Site-specific exclusion ranges
  capped_1795_archive <- ymd("2021-11-08", tz = "EST") #System 179-5 was capped for 2 months
  uncapped_1795_archive <- ymd("2021-12-30", tz = "EST")
  exclusion_1795_archive <- interval(start = capped_1795_archive, end = uncapped_1795_archive)
  
#Monitored sites, from prod
wells <- dbGetQuery(mars_prod, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid, g.gage_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id
                    left join admin.tbl_smp_gage g on o.smp_id = g.smp_id
                    where (o.ow_suffix like 'GI%' or o.ow_suffix = 'OW1')
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')") %>%
  filter(ow_uid != 1077) %>% #179-5-1 GI2 was not monitored 
  arrange(smp_id, ow_suffix)

#Are these the same in the archive DB?
wells_archive <- dbGetQuery(mars_archive, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid, g.gage_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id 
                    left join admin.tbl_smp_gage g on o.smp_id = g.smp_id
                    where (o.ow_suffix like 'GI%' or o.ow_suffix = 'OW1')
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')") %>%
  filter(ow_uid != 1077) %>% #179-5-1 GI2 was not monitored
  arrange(smp_id, ow_suffix)

if(!identical(wells, wells_archive)){
  stop("Fatal Error: GI query not identical across databases") #Halt everything if not.
}

#Read design storms from Brian's spreadsheet
sys_char_brian <- openxlsx::read.xlsx(xlsxFile = "//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/SystemCharacteristics.xlsx", sheet = "Characteristics") %>%
  transmute(smp_id, system_id, gi_suffix = GI, ow_suffix = OW, brian_design_storm_in = `Storm.Size.Managed.(in)`) %>%
  melt(id.vars = c("smp_id", "system_id", "brian_design_storm_in"), value.name = "ow_suffix") %>% #GI suffix and OW suffix stored in different variables; unifying them here
  select(smp_id, system_id, brian_design_storm_in) %>%
  unique %>%
  arrange(system_id)

#Read design storms from brian's archive database
sys_char_archive <- dbGetQuery(mars_archive, "select system_id, sys_rawstormsizemanaged_in as archive_rawssm_in, sys_creditedstormsizemanaged_in as archive_creditedssm_in from external.tbl_systembdv") %>% 
  filter(system_id %in% sys_char_brian$system_id) %>%
  mutate(smp_id = paste0(system_id, "-1")) %>%
  arrange(smp_id)

#Read design storms from prod
sys_char_prod <- dbGetQuery(mars_prod, "select system_id, sys_rawstormsizemanaged_in as prod_rawssm_in, sys_creditedstormsizemanaged_in prod_creditedssm_in from external.tbl_systembdv") %>% 
  filter(system_id %in% sys_char_brian$system_id) %>%
  mutate(smp_id = paste0(system_id, "-1")) %>%
  arrange(smp_id)

ssm <- left_join(sys_char_brian, sys_char_archive) %>% left_join(sys_char_prod)

#Attach storm size managed to the well table
#We will use Brian's, since it seems some have changed in the meantime
wells <- left_join(wells, ssm) %>% select(-system_id)

#Deployment depths from prod. Used for head diffs and OT calculations
deployment_depths_prod <- dbGetQuery(mars_prod, "select ow_uid, well_depth_ft, start_dtime, end_dtime, deployment_depth_ft from fieldwork.viw_ow_plus_measurements 
where ow_uid in(1165, 660, 1416, 663, 1415, 1157, 1413, 1065, 1414, 1066, 1076, 700, 1417, 1062, 1651, 1063)
and start_dtime < '2024-01-01'")

#Deployment depths from the archive
deployment_depths_archive <- dbGetQuery(mars_archive, "select ow_uid, well_depth_ft, start_dtime_est, end_dtime_est, deployment_depth_ft from fieldwork.viw_ow_plus_measurements 
where ow_uid in(1165, 660, 1416, 663, 1415, 1157, 1413, 1065, 1414, 1066, 1076, 700, 1417, 1062, 1651, 1063)
and start_dtime_est < '2024-01-01'")

```

## Background

In an effort to track down what differences and discrepancies exist between the data that Brian used for the 2024 VUSP Green Inlet Monitoring study, this document will perform a diff between an archival copy of the database he used and the current production MARS database for the same period.

Notable differences include the DST migration that took place in early 2025 and resulted in a retroactive springing-forwards of our water level data. The data structures in the MARS production database also contain time zone metadata. The 2024 archival database stores all timestamp data in implicit local time, with no time zone metadata, and reflects the responsiveness of that field to DST shifts in the name of the field (eg, dtime_est vs dtime_edt).

## Diffs 
```{r Raw counts level}

#Data points by OW
level_query_archive <- paste0("select l.dtime_est, l.level_ft, l.ow_uid, o.smp_id, o.ow_suffix 
                      from data.tbl_ow_leveldata_raw l
                      left join fieldwork.tbl_ow o on l.ow_uid = o.ow_uid
                      where l.ow_uid in (",
                      paste(wells$ow_uid, collapse = ", "),
                      ")")

level_archive <- dbGetQuery(mars_archive, level_query_archive) %>% 
  arrange(dtime_est) %>%
  filter(dtime_est < cutoff_date_archive) %>%
  filter(dtime_est >= start_date_archive) %>%
  filter(!(dtime_est >= cutoff_11_archive & smp_id == '1-1-1')) %>%
  filter(!(dtime_est >= cutoff_4391_archive & smp_id == '439-1-1')) %>%
  filter(!(dtime_est %within% exclusion_1795_archive & smp_id == '179-5-1'))

level_archive_summary <- group_by(level_archive, ow_uid, smp_id, ow_suffix) %>% 
  summarize(first = first(dtime_est), 
            last = last(dtime_est),
            count = n()) %>% 
  ungroup() %>%
  arrange(smp_id, ow_suffix)

level_query_prod <- paste0("select l.dtime, l.level_ft, l.ow_uid, o.smp_id, o.ow_suffix 
                      from data.tbl_ow_leveldata_raw l
                      left join fieldwork.tbl_ow o on l.ow_uid = o.ow_uid
                      where l.ow_uid in (",
                      paste(wells$ow_uid, collapse = ", "),
                      ")")

level_prod <- dbGetQuery(mars_prod, level_query_prod) %>%
  arrange(dtime) %>%
  filter(dtime < cutoff_date) %>%
  filter(dtime >= start_date) %>%
  filter(!(dtime >= cutoff_11 & smp_id == '1-1-1')) %>%
  filter(!(dtime >= cutoff_4391 & smp_id == '439-1-1')) %>%
  filter(!(dtime %within% exclusion_1795 & smp_id == '179-5-1'))

level_prod_summary <- group_by(level_prod, ow_uid, smp_id, ow_suffix) %>% 
  summarize(first = first(dtime), 
            last = last(dtime),
            count = n()) %>% 
  ungroup() %>%
  arrange(smp_id, ow_suffix)

```


```{r Raw counts rain, echo=FALSE}

#Oldest GI data in the analysis is from January 2019, so we will start measuring the rain from that date

radar_query_archive <- paste("select r.radar_uid, r.dtime_edt, r.rainfall_in from data.tbl_radar_rain r
  where dtime_edt > '2019-01-01 00:00:00' and radar_uid in (", paste(unique(wells$radar_uid), collapse = ", "), ")")
radar_archive <- dbGetQuery(mars_archive, radar_query_archive) %>% filter(dtime_edt < cutoff_date_archive)


radar_query_prod <- paste("select r.radar_uid, r.dtime, r.rainfall_in from data.tbl_radar_rain r
  where dtime > '2019-01-01 00:00:00' and radar_uid in (", paste(unique(wells$radar_uid), collapse = ", "), ")")
radar_prod <- dbGetQuery(mars_prod, radar_query_prod) %>% filter(dtime < cutoff_date)

```

```{r Raw counts events, echo=FALSE}

#Oldest GI data in the analysis is from January 2019, so we will start measuring the rain from that date

radar_event_query_archive <- paste0("select r.radar_event_uid, r.radar_uid, r.eventdatastart_edt, r.eventdataend_edt, r.eventduration_hr, r.eventpeakintensity_inhr, r.eventavgintensity_inhr, r.eventdepth_in from data.tbl_radar_event r
  where eventdatastart_edt > '2019-01-01 00:00:00'
    and radar_uid in (", paste(unique(wells$radar_uid), collapse = ', '), ")")
event_radar_archive <- dbGetQuery(mars_archive, radar_event_query_archive) %>% filter(eventdatastart_edt < cutoff_date_archive)

radar_event_query_prod <- paste0("select r.radar_event_uid, r.radar_uid, r.eventdatastart, r.eventdataend, r.eventduration_hr, r.eventpeakintensity_inhr, r.eventavgintensity_inhr, r.eventdepth_in from data.tbl_radar_event r
  where eventdatastart > '2019-01-01 00:00:00'
  and radar_uid in (", paste(unique(wells$radar_uid), collapse = ', '), ")")
event_radar_prod <- dbGetQuery(mars_prod, radar_event_query_prod) %>% filter(eventdatastart < cutoff_date)

#Event UIDs from Brian's metrics
archive_metrics_brian_dec15 <- read_csv("//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/2023-12-15/gi_metrics.csv")

archive_metrics_brian_jun10 <- read_csv("//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/2024-06-10/gi_metrics_5min.csv")

archive_metrics_brian_apr03 <- read_csv("//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis/2024-04-03/overtopping_data.csv")

#Radar summaries
event_summary_archive <- group_by(event_radar_archive, radar_uid) %>%
  summarize(count = n(), 
            totaldepth_in = sum(eventdepth_in), 
            totalduration_hr = sum(eventduration_hr),
            averageduration_hr = mean(eventduration_hr))

event_summary_prod <- group_by(event_radar_prod, radar_uid) %>%
  summarize(count = n(), 
            totaldepth_in = sum(eventdepth_in), 
            totalduration_hr = sum(eventduration_hr),
            averageduration_hr = mean(eventduration_hr))

```

```{r hypothetical event maxes, echo = FALSE}

# Create hypothetical per-site max counts of events for each data source
#Archive dataset
  radarmax_archive <- transmute(wells, ow_uid, smp_id, ow_suffix, radar_uid, archive_creditedssm_in, radarmax = NA)
  radarmax_archive_events <- data.frame(NULL)
  
  for(i in 1:nrow(radarmax_archive)){
    radar_events <- filter(event_radar_archive, radar_uid == radarmax_archive$radar_uid[i])
        print(paste(radarmax_archive$smp_id[i], "has", nrow(radar_events), "pre-exclusion events"))

    #Filter for exclusions
    if(radarmax_archive$smp_id[i] == '1-1-1'){
      radar_events <- filter(radar_events, eventdataend_edt < cutoff_11_archive)
    } else if(radarmax_archive$smp_id[i] == '439-1-1'){
      radar_events <- filter(radar_events, eventdataend_edt < cutoff_4391_archive)
    } else if(radarmax_archive$smp_id[i] == '179-5-1'){
      radar_events <- filter(radar_events, 
                             !(eventdatastart_edt %within% exclusion_1795_archive),
                             !(eventdataend_edt %within% exclusion_1795_archive))
  
    }
    
    #Filter for design storms only
      print(paste(radarmax_archive$smp_id[i], "has", nrow(radar_events), "post-exclusion events"))
    radar_events <- filter(radar_events, eventdepth_in <= radarmax_archive$archive_creditedssm_in[i])
      print(paste(radarmax_archive$smp_id[i], "has", nrow(radar_events), "post-exclusion design events"))

    radarmax_archive$radarmax[i] <- nrow(radar_events)
    radarmax_archive_events <- rbind(radarmax_archive_events, radar_events)
  }

#Prod dataset
  radarmax_prod <- transmute(wells, ow_uid, smp_id, ow_suffix, radar_uid, prod_creditedssm_in, radarmax = NA)
  radarmax_prod_events <- data.frame(NULL)
  for(i in 1:nrow(radarmax_prod)){
    radar_events <- filter(event_radar_prod, radar_uid == radarmax_prod$radar_uid[i])
        print(paste(radarmax_prod$smp_id[i], "has", nrow(radar_events), "pre-exclusion events"))


    #Filter for exclusions
    if(radarmax_prod$smp_id[i] == '1-1-1'){
      radar_events <- filter(radar_events, eventdataend < cutoff_11)
    } else if(radarmax_prod$smp_id[i] == '439-1-1'){
      radar_events <- filter(radar_events, eventdataend < cutoff_4391)
    } else if(radarmax_prod$smp_id[i] == '179-5-1'){
      radar_events <- filter(radar_events, 
                             !(eventdatastart %within% exclusion_1795),
                             !(eventdataend %within% exclusion_1795))
  
    }
    
    #Filter for design storms only
        print(paste(radarmax_prod$smp_id[i], "has", nrow(radar_events), "post-exclusion events"))
    radar_events <- filter(radar_events, eventdepth_in <= radarmax_prod$prod_creditedssm_in[i])
        print(paste(radarmax_prod$smp_id[i], "has", nrow(radar_events), "post-exclusion design events"))

    radarmax_prod$radarmax[i] <- nrow(radar_events)
    radarmax_prod_events <- rbind(radarmax_prod_events, radar_events)

  }
  
#How many per GI in Brian's archived metrics?
  radar_wellcounts_brian <- group_by(archive_metrics_brian_apr03, ow_uid) %>%
    summarize(count = n())
  
#compare with ark
  comparison <- left_join(radarmax_archive, radar_wellcounts_brian)
  
#how many per GI in Prod?
  comparison_prod <- left_join(radarmax_prod, radar_wellcounts_brian)

```

```{r empirically deriving brian's ssms, echo = FALSE}

  ranges <- seq(0.01, 3.00, 0.01)

  vuspvalues_brian <- tribble(~smp_id, ~n_vusp, ~mean_in_vusp, ~ot_vusp, ~percent_vusp,
                              "1-1-1", 116, 0.5, 36, 0.31,
                              "1-3-1", 149, 0.42, 4, 0.027,
                              "488-5-1", 123, 0.43, 4, 0.033,
                              "171-1-1", 132, 0.45, 8, 0.061,
                              "179-5-1", 144, 0.41, 13, 0.09,
                              "1006-1-1", 132, 0.44, 16, 0.121,
                              "171-2-1", 146, 0.42, 21, 0.144,
                              "439-1-1", 84, 0.39, 38, 0.452)

  wells_gi <- filter(wells, grepl("GI", ow_suffix)) %>% select(ow_uid, smp_id, ow_suffix, radar_uid)
  
  iterators <- data.frame(smp_id = c(rep("1-1-1",length(ranges)), 
                                    rep("1-3-1",length(ranges)), 
                                    rep("488-5-1",length(ranges)), 
                                    rep("171-1-1",length(ranges)), 
                                    rep("179-5-1",length(ranges)), 
                                    rep("1006-1-1",length(ranges)), 
                                    rep("171-2-1",length(ranges)), 
                                    rep("439-1-1",length(ranges))),
                          ssm = rep(ranges, 8),
                          stringsAsFactors = FALSE)
  
  wells_iterators <- left_join(wells_gi, iterators, by = "smp_id")
  
  summaries <- data.frame(NULL)
  
  for(i in 1:nrow(wells_iterators)){
    keys <- filter(archive_metrics_brian, ow_uid == wells_iterators$ow_uid[i])
    storms <- filter(event_radar_archive, radar_event_uid %in% keys$radar_event_uid)
    
    filtered_keys <- filter(storms, eventdepth_in <= wells_iterators$ssm[i])
    
    if(nrow(filtered_keys) == 0){ next }
    
    filtered_results <- filter(archive_metrics_brian_jun10, 
                               ow_uid == wells_iterators$ow_uid[i],
                               radar_event_uid %in% filtered_keys$radar_event_uid)
    
    summary <- group_by(filtered_results, ow_uid) %>%
      summarize(n = n(),
                mean_in = mean(filtered_keys$eventdepth_in),
                ot = sum(overtop),
                percent = ifelse(n() == 0, 0, ot/n()),
                ssm = wells_iterators$ssm[i])
    
    summaries <- rbind(summaries, summary)
    
  }
  
  bleed <- left_join(wells_iterators, summaries) %>%
    left_join(vuspvalues_brian)
  
  
  
```

```{r Testing Brian's various files, echo = FALSE}

  ranges <- seq(0.01, 3.00, 0.01)

  vuspvalues_brian <- tribble(~smp_id, ~n_vusp, ~mean_in_vusp, ~ot_vusp, ~percent_vusp,
                              "1-1-1", 116, 0.5, 36, 0.31,
                              "1-3-1", 149, 0.42, 4, 0.027,
                              "488-5-1", 123, 0.43, 4, 0.033,
                              "171-1-1", 132, 0.45, 8, 0.061,
                              "179-5-1", 144, 0.41, 13, 0.09,
                              "1006-1-1", 132, 0.44, 16, 0.121,
                              "171-2-1", 146, 0.42, 21, 0.144,
                              "439-1-1", 84, 0.39, 38, 0.452)

  wells_gi <- filter(wells, grepl("GI", ow_suffix)) %>% select(ow_uid, smp_id, ow_suffix)
  
  iterators <- data.frame(smp_id = c(rep("1-1-1",length(ranges)), 
                                    rep("1-3-1",length(ranges)), 
                                    rep("488-5-1",length(ranges)), 
                                    rep("171-1-1",length(ranges)), 
                                    rep("179-5-1",length(ranges)), 
                                    rep("1006-1-1",length(ranges)), 
                                    rep("171-2-1",length(ranges)), 
                                    rep("439-1-1",length(ranges))),
                          ssm = rep(ranges, 8),
                          stringsAsFactors = FALSE)
  
  wells_iterators <- left_join(wells_gi, iterators, by = "smp_id")

  searchfolder <- "//pwdoows/OOWS/Watershed Sciences/GSI Monitoring/06 Special Projects/40 Green Inlet Monitoring/MARS Analysis"

  testfolders <- list.files(path = searchfolder, pattern = "^\\d{3}[34]", include.dirs = TRUE, full.names=TRUE)
  
  folderframe <- data.frame(folder = testfolders,
                            otfile = NA,
                            summaryfile = NA)
  
  for(i in 1:nrow(folderframe)){
    # gifile <- list.files(folderframe$folder[i], pattern = "gi_metrics", full.names=TRUE)
    # folderframe$gifile[i] <- ifelse(length(gifile == 0), NA, gifile)

    otfile <- list.files(folderframe$folder[i], pattern = "overtopping_data", full.names=TRUE)
    folderframe$otfile[i] <- ifelse(length(otfile) == 0, NA, otfile)
    
    summaryfile <- list.files(folderframe$folder[i], pattern = "gi_design_storm_summary", full.names=TRUE)
    folderframe$summaryfile[i] <- ifelse(length(summaryfile)==0, NA, summaryfile)
  }
  
  folderframe <- folderframe[complete.cases(folderframe),]
  
  folderresults <- list(NULL)
  
  for(i in 1:nrow(folderframe)){
    otresults <- read_csv(folderframe$otfile[i])
    #giresults <- read_csv(folderframe$gifile[i])
    folderresult <- list(NULL)
    summaries <- data.frame(NULL)
    
    for(j in 1:nrow(wells_iterators)){
      ot_well <- filter(otresults, ow_uid == wells_iterators$ow_uid[j])
      ot_filtered <- filter(ot_well, eventdepth_in <= wells_iterators$ssm[j])
      
      if(length(ot_filtered) == 0){ next }
      
      summary <- group_by(ot_filtered, ow_uid) %>%
        summarize(n = n(),
                  mean_in = mean(eventdepth_in),
                  ot = sum(overtop),
                  percent = ifelse(n() == 0, 0, ot/n()),
                  ssm = wells_iterators$ssm[j])
      
      summaries <- rbind(summaries, summary)
    }
    
    folderresult[["SSMTest_ot"]] <- summaries

    folderresult[["SummaryFile"]] <- read_csv(folderframe$summaryfile[i])

    folderresults[[basename(folderframe$folder[i])]] <- folderresult
        
  }

  onepointthree <- list(NULL)
  for(i in 2:length(folderresults)){
    a <- list(NULL)
    a[[1]] <- filter(folderresults[[i]]$SSMTest_ot, ssm == 1.3) %>% arrange(percent)
    a[[2]] <- folderresults[[i]]$SummaryFile %>% 
      arrange(overtop_perc)
    onepointthree[[names(folderresults)[i]]] <- a
  }
  
```

```{r brians calcs with correct ssm, echo = FALSE}

ssm_archive <- dbGetQuery(mars_archive, "select system_id, sys_creditedstormsizemanaged_in from external.tbl_systembdv")

brians_resultsfile <- folderframe$otfile[2]
brians_results <- read_csv(brians_resultsfile)

brianswells <- select(brians_results, ow_uid, smp_id) %>%
  mutate(system_id = gsub("-1$", "", smp_id)) %>%
  unique %>%
  left_join(ssm_archive)

summaries <- data.frame(NULL)

for(i in 1:nrow(brianswells)){
  ot_well <- filter(brians_results, ow_uid == brianswells$ow_uid[i])
  ot_filtered <- filter(ot_well, eventdepth_in <= brianswells$sys_creditedstormsizemanaged_in[i])
      
  if(length(ot_filtered) == 0){ next }
      
    summary <- group_by(ot_filtered, ow_uid) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              overtop = sum(overtop),
              percent = ifelse(n() == 0, 0, overtop/n() * 100),
              ssm = brianswells$sys_creditedstormsizemanaged_in[i])
      
    summaries <- rbind(summaries, summary)
}

summaries #What brian's results would have been at VUSP if he had used the correct SSMs

```

```{r brians calcs with modern ssm, echo = FALSE}

ssm_prod <- dbGetQuery(mars_prod, "select system_id, sys_creditedstormsizemanaged_in from external.tbl_systembdv")

brians_resultsfile <- folderframe$otfile[2]
brians_results <- read_csv(brians_resultsfile)

brianswells_prod <- select(brians_results, ow_uid, smp_id) %>%
  mutate(system_id = gsub("-1$", "", smp_id)) %>%
  unique %>%
  left_join(ssm_prod)

summaries_prod <- data.frame(NULL)

for(i in 1:nrow(brianswells_prod)){
  ot_well <- filter(brians_results, ow_uid == brianswells_prod$ow_uid[i])
  ot_filtered <- filter(ot_well, eventdepth_in <= brianswells_prod$sys_creditedstormsizemanaged_in[i])
      
  if(length(ot_filtered) == 0){ next }
      
    summary <- group_by(ot_filtered, ow_uid) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              overtop = sum(overtop),
              percent = ifelse(n() == 0, 0, overtop/n() * 100),
              ssm = brianswells_prod$sys_creditedstormsizemanaged_in[i])
      
    summaries_prod <- rbind(summaries, summary)
}

summaries_prod #What brian's results would have been at VUSP if he had used the SSMs on prod today

```

```{r OT on prod, echo = FALSE}
  
  #GI Overtopping
  wells_gi <- filter(wells, grepl("GI", ow_suffix)) %>% 
    left_join(deployment_depths_prod) %>%
    select(ow_uid, smp_id, ow_suffix, radar_uid, deployment_depth_ft, prod_creditedssm_in)

  overtopping_prod <- data.frame(NULL)

  #For each site
  for(i in 1:nrow(wells_gi)){
  #for(i in 2){  
    sitelevel <- filter(level_prod, ow_uid == wells_gi$ow_uid[i]) %>% arrange(dtime)
    siteevents <- filter(event_radar_prod, radar_uid == wells_gi$radar_uid[i])
    
    #For each event
    for(j in 1:nrow(siteevents)){
    #for(j in 1){
      #Start: event start time
      event_start <- siteevents$eventdatastart[j]
      
      #End: Event end time + 24 hours or event N+1 start time, whichever is shorter
      event_end <- ifelse(is.na(siteevents$eventdataend[j+1]), #If we are on the last event
                          event_start+hours(24), #End the series 24 hours later
                          min(event_start+hours(24), siteevents$eventdataend[j+1]))
                            #If there are more events in the future, min of these two values
      
      #Filter to GI time series for that event
      eventlevel <- filter(sitelevel, dtime %within% interval(event_start, event_end))
      
      #If there is no data, report that and skip
      if(nrow(eventlevel) == 0){
        event_results <- data.frame(ow_uid = wells_gi$ow_uid[i],
                                    radar_event_uid = siteevents$radar_event_uid[j],
                                    eventdepth_in = siteevents$eventdepth_in[j],
                                    event_start = event_start,
                                    event_end = siteevents$eventdataend[j],
                                    level_end = NA_POSIXct_,
                                    overtop = NA,
                                    max_level_ft = NA,
                                    event_max = NA_POSIXct_,
                                    deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                                    note = "No level data present in GI time series for this event")
        
        overtopping_prod <- rbind(overtopping_prod, event_results)
        next
      }
      #browser()
      #Call mars overtopping function with TS + GI deployment depth
      event_results <- data.frame(ow_uid = wells_gi$ow_uid[i],
                            radar_event_uid = siteevents$radar_event_uid[j],
                            eventdepth_in = siteevents$eventdepth_in[j],
                            event_start = event_start,
                            event_end = siteevents$eventdataend[j],
                            level_end = event_end,
                            overtop = marsOvertoppingCheck_bool(
                              waterlevel_ft = eventlevel$level_ft,
                              storage_depth_ft = wells_gi$deployment_depth_ft[i]),
                            max_level_ft = max(eventlevel$level_ft),
                            event_max = first(eventlevel$dtime[which(eventlevel$level_ft == max(eventlevel$level_ft))]),
                            deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                            note = NA)
      
      overtopping_prod <- rbind(overtopping_prod, event_results)
    }
      
  }

  ot_full_prod <- left_join(overtopping_prod, wells_gi)
  ot_full_prod_summary <- group_by(ot_full_prod, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop), na.rm = TRUE),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
  
  ot_design_prod <- filter(ot_full_prod, !is.na(overtop), eventdepth_in <= prod_creditedssm_in)
  ot_design_prod_summary <- group_by(ot_design_prod, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop)),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
  

```

```{r HD on prod, echo = FALSE}

  #For each site
    #For each event
    #Filter to GI and OW time series for that event
      #Start: event start time
      #End: Event end time + 72 hours or event N+1 start time, whichever is shorter

    #Find max water level for GI during that series
    #Find corresponding level in OW at that time (if not exact, closest point in time)

```

```{r OT on archive reproducing Brian's bugs}
  #GI Overtopping
  wells_gi <- filter(wells, grepl("GI", ow_suffix)) %>% 
    left_join(deployment_depths_archive) %>%
    select(ow_uid, smp_id, ow_suffix, radar_uid, deployment_depth_ft, archive_creditedssm_in)

  overtopping_archive <- data.frame(NULL)

  #For each site
  for(i in 1:nrow(wells_gi)){
  #for(i in 1){  
    sitelevel_archive <- filter(level_archive, ow_uid == wells_gi$ow_uid[i]) %>% arrange(dtime_est)
    siteevents_archive <- filter(event_radar_archive, radar_uid == wells_gi$radar_uid[i])
    
    #Filter for exclusions
    if(wells_gi$smp_id[i] == '1-1-1'){
      siteevents_archive <- filter(siteevents_archive, eventdataend_edt < cutoff_11_archive)
      siteevents_archive <- filter(siteevents_archive, eventdataend_edt < ymd('2020-09-11', tz = "EST")) #Reproduced bug: Brian's 1-1-1 GI1 data stops at 9/10/2023ot_ 
    } else if(wells_gi$smp_id[i] == '439-1-1'){
      siteevents_archive <- filter(siteevents_archive, eventdataend_edt < cutoff_4391_archive)
    } else if(wells_gi$smp_id[i] == '179-5-1'){
      siteevents_archive <- filter(siteevents_archive, 
                             !(eventdatastart_edt %within% exclusion_1795_archive),
                             !(eventdataend_edt %within% exclusion_1795_archive))
  
    }
    
    #For each event
    for(j in 1:nrow(siteevents_archive)){
      
    #for(j in 5){
      #Start: event start time
      event_start_archive <- siteevents_archive$eventdatastart_edt[j]
      
      #End: Event end time + 24 hours or event N+1 start time, whichever is shorter
      event_end_archive <- ifelse(is.na(siteevents_archive$eventdataend_edt[j+1]), #If we are on the last event
                          event_start_archive+hours(24), #End the series 24 hours later
                          min(event_start_archive+hours(24), siteevents_archive$eventdataend_edt[j+1]))
                            #If there are more events in the future, min of these two values
      
      if(event_start_archive >= ymd('2024-05-01', tz = "EST")){
        next #Reproduced bug: Data not available after April 30th 2023
      }
      
      #Filter to GI time series for that event
      eventlevel_archive <- filter(sitelevel_archive, dtime_est %within% interval(event_start_archive, event_end_archive))
      
      #If there is no data, report that and skip
      if(nrow(eventlevel_archive) == 0){
        event_results_archive <- data.frame(ow_uid = wells_gi$ow_uid[i],
                                    radar_event_uid = siteevents_archive$radar_event_uid[j],
                                    eventdepth_in = siteevents_archive$eventdepth_in[j],
                                    event_start = event_start_archive,
                                    event_end = siteevents_archive$eventdataend_edt[j],
                                    level_end = NA_POSIXct_,
                                    overtop = NA,
                                    max_level_ft = NA,
                                    event_max = NA_POSIXct_,
                                    deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                                    note = "No level data present in GI time series for this event")
        
        overtopping_archive <- rbind(overtopping_archive, event_results_archive)
        next
      }
        
      #Call mars overtopping function with TS + GI deployment depth
      event_results_archive <- data.frame(ow_uid = wells_gi$ow_uid[i],
                            radar_event_uid = siteevents_archive$radar_event_uid[j],
                            eventdepth_in = siteevents_archive$eventdepth_in[j],
                            event_start = event_start_archive,
                            event_end = siteevents_archive$eventdataend_edt[j],
                            level_end = event_end,
                            overtop = marsOvertoppingCheck_bool(
                              waterlevel_ft = eventlevel_archive$level_ft,
                              storage_depth_ft = wells_gi$deployment_depth_ft[i]),
                            max_level_ft = max(eventlevel_archive$level_ft),
                            event_max = first(eventlevel_archive$dtime_est[which(eventlevel_archive$level_ft == max(eventlevel_archive$level_ft))]),
                            deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                            note = NA)
      
      overtopping_archive <- rbind(overtopping_archive, event_results_archive)
      
    }
      
  }
  
  ot_full_archive <- left_join(overtopping_archive, wells_gi)
  ot_full_archive_summary <- group_by(ot_full_archive, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop), na.rm = TRUE),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
  
  
  ot_design_archive <- filter(ot_full_archive, !is.na(overtop), eventdepth_in <= 1.3)#archive_creditedssm_in)
  ot_design_archive_summary <- group_by(ot_design_archive, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop)),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
    
  
  #plot them
  for(i in 1:nrow(wells_gi)){
    
    reproduced_events <- filter(ot_full_archive, ow_uid == wells_gi$ow_uid[i]) %>% filter(!is.na(overtop))
    
    events_brian <- filter(archive_metrics_brian_apr03, ow_uid == wells_gi$ow_uid[i])
    
    label_position_x <- ifelse(nrow(reproduced_events) %% 2 == 0, 
                               nrow(reproduced_events)*3/4, 
                               (nrow(reproduced_events) + 1)*3/4)
    
    scatter <- ggplot() +
      geom_point(data = reproduced_events, 
                 aes(x = event_start, y = eventdepth_in, shape = "Archive Reproduction", color = overtop)) + 
      geom_point(data = events_brian, 
                 aes(x = eventdatastart_edt, y = eventdepth_in, shape = "Brian's Apr 03 CSV", color = overtop)) + 
      scale_shape_manual(values = c(4, 20)) + 
      geom_hline(yintercept = 1.3) +
      geom_label(data = data.frame(x = reproduced_events$event_start[label_position_x], y = 1.3, label = "Erroneous 1.3in Design Storm"),
                 aes(x = x, y = y, label = label)) +
      ggtitle(paste(wells_gi$smp_id[i], wells_gi$ow_suffix[i], "Reproduced OT Events")) +
      xlab("Rain Event Start Date") +
      ylab("Rain Event Depth (inches)") +
      labs(shape = "Data Source")+ 
      theme(plot.title = element_text(size = 26),
            axis.title = element_text(size = 26),
            axis.text = element_text(size = 20),
            legend.title = element_text(size = 26),
            legend.text = element_text(size = 20)) +
      guides(shape = guide_legend(override.aes = list(size = 5))) +
      ylim(0, 1.5)
    
    
    ggsave(paste(wells_gi$smp_id[i], wells_gi$ow_suffix[i], "Reproduced OT Events.png"),
           scatter,
           width = 12,
           height = 8,
           units = "in",
           dpi = 300)
    
  }
  
  

```

```{r OT on archive using my code}
  #GI Overtopping
  wells_gi <- filter(wells, grepl("GI", ow_suffix)) %>% 
    left_join(deployment_depths_archive) %>%
    select(ow_uid, smp_id, ow_suffix, radar_uid, deployment_depth_ft, archive_creditedssm_in)

  overtopping_archive <- data.frame(NULL)

  #For each site
  for(i in 1:nrow(wells_gi)){
  #for(i in 1){  
    sitelevel_archive <- filter(level_archive, ow_uid == wells_gi$ow_uid[i]) %>% arrange(dtime_est)
    siteevents_archive <- filter(event_radar_archive, radar_uid == wells_gi$radar_uid[i])
    
    #For each event
    for(j in 1:nrow(siteevents_archive)){
    #for(j in 5){
      #Start: event start time
      event_start_archive <- siteevents_archive$eventdatastart_edt[j]
      
      #End: Event end time + 24 hours or event N+1 start time, whichever is shorter
      event_end_archive <- ifelse(is.na(siteevents_archive$eventdataend_edt[j+1]), #If we are on the last event
                          event_start_archive+hours(24), #End the series 24 hours later
                          min(event_start_archive+hours(24), siteevents_archive$eventdataend_edt[j+1]))
                            #If there are more events in the future, min of these two values
      
      #Filter to GI time series for that event
      eventlevel_archive <- filter(sitelevel_archive, dtime_est %within% interval(event_start_archive, event_end_archive))
      
      #If there is no data, report that and skip
      if(nrow(eventlevel_archive) == 0){
        event_results_archive <- data.frame(ow_uid = wells_gi$ow_uid[i],
                                    radar_event_uid = siteevents_archive$radar_event_uid[j],
                                    eventdepth_in = siteevents_archive$eventdepth_in[j],
                                    event_start = event_start_archive,
                                    event_end = siteevents_archive$eventdataend_edt[j],
                                    level_end = NA_POSIXct_,
                                    overtop = NA,
                                    max_level_ft = NA,
                                    event_max = NA_POSIXct_,
                                    deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                                    note = "No level data present in GI time series for this event")
        
        overtopping_archive <- rbind(overtopping_archive, event_results_archive)
        next
      }
        
      #Call mars overtopping function with TS + GI deployment depth
      event_results_archive <- data.frame(ow_uid = wells_gi$ow_uid[i],
                            radar_event_uid = siteevents_archive$radar_event_uid[j],
                            eventdepth_in = siteevents_archive$eventdepth_in[j],
                            event_start = event_start,
                            event_end = siteevents_archive$eventdataend_edt[j],
                            level_end = event_end,
                            overtop = marsOvertoppingCheck_bool(
                              waterlevel_ft = eventlevel_archive$level_ft,
                              storage_depth_ft = wells_gi$deployment_depth_ft[i]),
                            max_level_ft = max(eventlevel_archive$level_ft),
                            event_max = first(eventlevel_archive$dtime_est[which(eventlevel_archive$level_ft == max(eventlevel_archive$level_ft))]),
                            deployment_depth_ft = wells_gi$deployment_depth_ft[i],
                            note = NA)
      
      overtopping_archive <- rbind(overtopping_archive, event_results_archive)
    }
      
  }
  
  ot_full_archive <- left_join(overtopping_archive, wells_gi)
  ot_full_archive_summary <- group_by(ot_full_archive, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop), na.rm = TRUE),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
  
  
  ot_design_archive <- filter(ot_full_archive, !is.na(overtop), eventdepth_in <= archive_creditedssm_in)
  ot_design_archive_summary <- group_by(ot_design_archive, smp_id) %>%
    summarize(mean_in = mean(eventdepth_in),
              n = n(),
              ot = sum(as.logical(overtop)),
              percent = ifelse(n() == 0, NA, ot/n)) %>%
    arrange(percent)
    

```

```{r Set size comparison, echo = FALSE}

  extra_level <- data.frame(NULL)
  
  for(i in 1:nrow(wells)){
  #for(i in 3){
    well_archive <- filter(level_archive, ow_uid == wells$ow_uid[i])
    
    well_archive_bumped <- well_archive %>% 
      mutate(dtime = with_tz(round_date(dtime_est, unit = "minute"), tzone = "America/New_York")) %>%
      filter(!duplicated(dtime))
    
    well_prod <- filter(level_prod, ow_uid == wells$ow_uid[i])
    
    overlap <- left_join(well_prod, well_archive_bumped, by = c("dtime", "ow_uid", "smp_id", "ow_suffix"), suffix = c(".prod", ".archive"))
    
    exceedence <- filter(overlap, is.na(level_ft.archive))
    
    extra_level <- rbind(extra_level, exceedence)
  }

  extra_level_summary <- extra_level %>% 
    group_by(ow_uid, smp_id, ow_suffix) %>% 
    summarize(n = n(), 
              first = first(dtime),
              last = last(dtime)) %>%
    arrange(smp_id)
  
  ggplot(data = extra_level, aes(x = dtime, y = level_ft.prod, color = ow_uid)) + geom_point()
  
  #radar events
  
  
  
  for(i in 1:nrow(wells)){
    events_archive <- filter(event_radar_archive, radar_uid == wells$radar_uid[i]) #No need to bump, they are responsive to DST already
    
    events_prod <- filter(event_radar_prod, radar_uid == wells$radar_uid[i])
    
    events_brian <- filter(archive_metrics_brian_apr03, radar_uid == wells$radar_uid[i])
    
    label_position_x <- ifelse(nrow(events_archive) %% 2 == 0, 
                               nrow(events_archive)*3/4, 
                               (nrow(events_archive) + 1)*3/4)
    
    scatter <- ggplot() +
      geom_point(data = events_prod, 
                 aes(x = eventdatastart, y = eventdepth_in, shape = "Production DB"),
                 color = "#D55E00") + 
      geom_point(data = events_archive, 
                 aes(x = eventdatastart_edt, y = eventdepth_in, shape = "Archive DB"), 
                 color = "#009E73") + 
      scale_shape_manual(values = c(4, 20)) + 
      geom_hline(yintercept = 1.3) +
      geom_label(data = data.frame(x = events_archive$eventdatastart_edt[label_position_x], y = 1.3, label = "Erroneous 1.3in Design Storm"),
                 aes(x = x, y = y, label = label)) +
      ggtitle(paste(wells$smp_id[i], wells$ow_suffix[i], "Radar Events: 2024-04-05 Archive vs Prod")) +
      xlab("Rain Event Start Date") +
      ylab("Rain Event Depth (inches)") +
      labs(shape = "Data Source")+ 
      theme(plot.title = element_text(size = 26),
            axis.title = element_text(size = 26),
            axis.text = element_text(size = 20),
            legend.title = element_text(size = 26),
            legend.text = element_text(size = 20)) +
      guides(shape = guide_legend(override.aes = list(size = 5)))
    
    
    ggsave(paste(wells$smp_id[i], wells$ow_suffix[i], "Radar Events.png"),
           scatter,
           width = 16,
           height = 8,
           units = "in",
           dpi = 300)
    
    scatter_zoom <- scatter + 
      scale_x_datetime(date_labels = "%b %Y", 
                       limits = c(ymd_hms('2023-01-01 00:00:00'), ymd_hms('2024-01-01 00:00:00')))
    
      ggsave(paste(wells$smp_id[i], wells$ow_suffix[i], "2023 Radar Events.png"),
           scatter_zoom,
           width = 16,
           height = 8,
           units = "in",
           dpi = 300)
  }

```
