---
title: "Database Diffs"
output: html_document
date: "2025-09-22"
---

```{r setup, include=FALSE}

#Dplyr stuff
library(magrittr)
library(tidyverse)
library(lubridate)
library(knitr)

#Database Stuff
library(pool)
library(RPostgres)

#Brian's archival database
mars_brian <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "gi_20240614",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)},
  error = function(e){e})

#Live database
mars_prod <- tryCatch({
  dbPool(
    drv = RPostgres::Postgres(),
    host = "PWDMARSDBS1",
    port = 5434,
    dbname = "mars_prod",
    user= Sys.getenv("admin_uid"),
    password = Sys.getenv("admin_pwd"),
    timezone = NULL)},
  error = function(e){e})

#Calculation data ranges
  #Basic cutoff date
  cutoff_date <- ymd("2024-01-01", tz = "America/New_York") #Original analysis was through 2023
  
  #Site-specific cutoff dates
  cutoff_11 <- ymd("2020-11-13", tz = "America/New_York") #System 1-1 taken offline for short-circuiting
  cutoff_4391 <- ymd("2022-01-14", tz = "America/New_York") #System 439-1 taken offline for short-circuiting
  
  #Site-specific exclusion ranges
  capped_1795 <- ymd("2021-11-08", tz = "America/New_York") #System 179-5 was capped for 2 months
  uncapped_1795 <- ymd("2021-12-30", tz = "America/New_York")
  exclusion_1795 <- interval(start = capped_1795, end = uncapped_1795)

#Monitored sites, from prod
wells <- dbGetQuery(mars_prod, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid, g.gage_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id
                    left join admin.tbl_smp_gage g on o.smp_id = g.smp_id
                    where (o.ow_suffix like 'GI%' or o.ow_suffix = 'OW1')
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')") %>%
  filter(ow_uid != 1077) %>% #179-5-1 GI2 was not monitored 
  arrange(smp_id, ow_suffix)

#Are these the same in Brian's DB?
wells_brian <- dbGetQuery(mars_brian, "select ow_uid, o.smp_id, ow_suffix, r.radar_uid, g.gage_uid from fieldwork.tbl_ow o 
                    left join admin.tbl_smp_radar r on o.smp_id = r.smp_id 
                    left join admin.tbl_smp_gage g on o.smp_id = g.smp_id
                    where (o.ow_suffix like 'GI%' or o.ow_suffix = 'OW1')
                      and o.smp_id in ('1-1-1', '1-3-1', '171-1-1', '171-2-1', '179-5-1', '439-1-1', '488-5-1', '1006-1-1')") %>%
  filter(ow_uid != 1077) %>% #179-5-1 GI2 was not monitored
  arrange(smp_id, ow_suffix)

if(!identical(wells, wells_brian)){
  stop("Fatal Error: GI query not identical across databases") #Halt everything if not.
}


```

## Background

In an effort to track down what differences and discrepancies exist between the data that Brian used for the 2024 VUSP Green Inlet Monitoring study, this document will perform a diff between an archival copy of the database he used and the current production MARS database for the same period.

Notable differences include the DST migration that took place in early 2025 and resulted in a retroactive springing-forwards of our water level data. The data structures in the MARS production database also contain time zone metadata. The 2024 archival database stores all timestamp data in implicit local time, with no time zone metadata, and reflects the responsiveness of that field to DST shifts in the name of the field (eg, dtime_est vs dtime_edt).

```{r Raw counts level}

#Data points by OW
level_query_brian <- paste0("select l.dtime_est, l.level_ft, l.ow_uid, o.smp_id, o.ow_suffix 
                      from data.tbl_ow_leveldata_raw l
                      left join fieldwork.tbl_ow o on l.ow_uid = o.ow_uid
                      where l.ow_uid in (",
                      paste(wells$ow_uid, collapse = ", "),
                      ")")

level_brian <- dbGetQuery(mars_brian, level_query_brian) #%>%

beep <- level_brian %>% arrange(dtime_est) %>%
  filter(dtime_est < cutoff_date) %>%
  filter(!(dtime_est >= cutoff_11 & smp_id == '1-1-1')) %>%
  filter(!(dtime_est >= cutoff_4391 & smp_id == '439-1-1')) %>%
  filter(!(dtime_est %within% exclusion_1795 & smp_id == '179-5-1'))

bope <- group_by(beep, ow_uid, smp_id, ow_suffix) %>% 
  summarize(first = first(dtime_est), 
            last = last(dtime_est),
            count = n()) %>% 
  ungroup() %>%
  arrange(smp_id, ow_suffix)

level_query_prod <- paste0("select l.dtime, l.level_ft, l.ow_uid, o.smp_id, o.ow_suffix 
                      from data.tbl_ow_leveldata_raw l
                      left join fieldwork.tbl_ow o on l.ow_uid = o.ow_uid
                      where l.ow_uid in (",
                      paste(wells$ow_uid, collapse = ", "),
                      ")")

level_prod <- dbGetQuery(mars_prod, level_query_prod) #%>%
bape <- level_prod %>% arrange(dtime) %>%
  filter(dtime < cutoff_date) %>%
  filter(!(dtime >= cutoff_11 & smp_id == '1-1-1')) %>%
  filter(!(dtime >= cutoff_4391 & smp_id == '439-1-1')) %>%
  filter(!(dtime %within% exclusion_1795 & smp_id == '179-5-1'))

barp <- group_by(bape, ow_uid, smp_id, ow_suffix) %>% 
  summarize(first = first(dtime), 
            last = last(dtime),
            count = n()) %>% 
  ungroup() %>%
  arrange(smp_id, ow_suffix)

```


```{r Raw counts rain, echo=FALSE}

#Oldest GI data in the analysis is from January 2019, so we will start measuring the rain from that date

gage_query_brian <- "select r.gage_uid, r.dtime_edt, r.rainfall_in from data.tbl_gage_rain r
  where dtime_edt > '2019-01-01 00:00:00'"
gage_brian <- dbGetQuery(mars_brian, gage_query_brian) %>% filter(dtime_edt < cutoff_date)

radar_query_brian <- "select r.radar_uid, r.dtime_edt, r.rainfall_in from data.tbl_radar_rain r
  where dtime_edt > '2019-01-01 00:00:00'"
radar_brian <- dbGetQuery(mars_brian, radar_query_brian) %>% filter(dtime_edt < cutoff_date)

gage_query_prod <- "select r.gage_uid, r.dtime, r.rainfall_in from data.tbl_gage_rain r
  where dtime > '2019-01-01 00:00:00'"
gage_prod <- dbGetQuery(mars_prod, gage_query_prod) %>% filter(dtime < cutoff_date)

radar_query_prod <- "select r.radar_uid, r.dtime, r.rainfall_in from data.tbl_radar_rain r
  where dtime > '2019-01-01 00:00:00'"
radar_prod <- dbGetQuery(mars_prod, radar_query_prod) %>% filter(dtime < cutoff_date)


```
